Proposal to improve BBC Search through the use of Linked Data

### 2014-05-05 chapter2.tex
Made some start to chapter 3 and proved getting graphviz working for embedded diagrams.
Removed bad reference and started building up an abstract diagram of the indexing chain.

In section~\ref{linked-enterprise-data} and section~\ref{reasoning}, I will
outline some of the linked data approaches and techniques that relate to
working with data models themselves.

@@

In recent years, a growing trend has emerged to use
Linked Data in the enterprise to remove the need
for repeated integration projects or data warehousing.
indexes over bespoke integration efforts. This follows from
a major motivation of Linked Data being that it aids in breaking
down information silos. \cite{bizer2009linked} In the
\emph{Linked Enterprise Data} approach, all information
production remains \emph{distributed} but is
\emph{connectable}.\cite{allemang2010semantic}

>>>>

@@

In recent years, a growing trend has emerged to use
Linked Data in the enterprise to remove the need
for repeated integration projects or data warehousing.
indexes over bespoke integration efforts. This follows from
a major motivation of Linked Data being that it aids in breaking
down information silos.\cite{bizer2009linked} In the
\emph{Linked Enterprise Data} approach, all information
production remains \emph{distributed} but is
\emph{connectable}.\cite{allemang2010semantic}
